### 2008-03-01 SAiP/Module1/H3/doc/architecturaldescription.tex
Formatting of questions completed.

%%%
% Architectural Description
%%%
\subsection{Architectural Description -- Beer Web Store}
The architect for a new Beer Web Store for specialty beers has drawn
the following figure of the architecture together with his customers.
\begin{figure}[h!]
  \centerline{\epsfig{figure=figures/beerstore,scale=0.30,clip=true}}
\end{figure}
The system is to support web users that may purchase beers using a web
browser. The system runs on top of a database (``DB''), contains
domain model (``Data''), an overview page (``Overview''), and a
``Basket'' subpart.

Discuss:
\begin{itemize}
    \item Which structures does a system such as the above exhibit?
    Give examples of elements and relations pertaining to each
    structure
    \item Which viewpoints are relevant when describing the example?
    Give examples of partials views for each viewpoint
    \item Argue for benefits and liabilities of describing software
    architecture via a box-and-line drawing such as the above
    \item Discuss what architectural description would be needed if
    the system was to be realized as a Service-Oriented Architecture
\end{itemize}

>>>>

%%%
% Architectural Description
%%%
\section{Architectural Description -- Beer Web Store}

The architect for a new Beer Web Store for specialty beers has drawn
the following figure of the architecture together with his customers.
\begin{figure}[h!]
  \centerline{\epsfig{figure=figures/beerstore,scale=0.30,clip=true}}
\end{figure}
The system is to support web users that may purchase beers using a web
browser. The system runs on top of a database (``DB''), contains
domain model (``Data''), an overview page (``Overview''), and a
``Basket'' subpart.

\subsection{Architectural Description - Question 1}

\begin{question}
Which structures does a system such as the above exhibit?
Give examples of elements and relations pertaining to each
structure
\end{question}

\fixme{Answer question 2.1}

\subsection{Architectural Description - Question 2}

\begin{question}
Which viewpoints are relevant when describing the example?
Give examples of partials views for each viewpoint
\end{question}

\fixme{Answer question 2.2}

\subsection{Architectural Description - Question 3}

\begin{question}
Argue for benefits and liabilities of describing software
architecture via a box-and-line drawing such as the above
\end{question}

\fixme{Answer question 2.3}

\subsection{Architectural Description - Question 4}

\begin{question}
Discuss what architectural description would be needed if
the system was to be realized as a Service-Oriented Architecture
\end{question}

\fixme{Answer question 2.4}

### 2008-03-01 SAiP/Module1/H3/doc/productlines.tex
Formatting of questions completed.

%%%
% Product Lines and Frameworks
%%%
\subsection{Product Lines -- Beer Web Store}
Consider a Beer Web Store for buying specialty beers. The software
architect has designed a deployment structure of the system as shown
below:
\begin{figure}[h!]
  \centerline{\epsfig{figure=figures/bws-deployment,scale=0.80}}
  \label{fig:observation}
\end{figure}
The main architectural drivers for the system are performance and
modifiability and the following is the main use case for the system:
\begin{quote}
  The customer browses the beer catalogue for descriptions and
  reviews. The customer selects appropriate beers for purchase and
  these are added to his shopping basket. When the customer checks
  out, payment is validated through the payment service
\end{quote}

@@

Discuss:
\begin{itemize}
\item How will the choice of a product line approach affect the
  architecture of the beer web store?
  \item Discuss the benefits and liabilities of using a product line
    approach in relation to the case?
  \item Relate Service-Oriented Architecture and Product Lines?
\end{itemize}

>>>>

%%%
% Product Lines and Frameworks
%%%
\section{Product Lines -- Beer Web Store}
Consider a Beer Web Store for buying specialty beers. The software
architect has designed a deployment structure of the system as shown
below:
\begin{figure}[h!]
  \centerline{\epsfig{figure=figures/bws-deployment,scale=0.80}}
  \label{fig:observation}
\end{figure}
The main architectural drivers for the system are performance and
modifiability and the following is the main use case for the system:
\begin{quote}
  The customer browses the beer catalogue for descriptions and
  reviews. The customer selects appropriate beers for purchase and
  these are added to his shopping basket. When the customer checks
  out, payment is validated through the payment service
\end{quote}

@@

\subsection{Product Lines - Question 1}

\begin{question}
How will the choice of a product line approach affect the
architecture of the beer web store?
\end{question}

\fixme{Answer question 5.1}

\subsection{Product Lines - Question 2}

\begin{question}
Discuss the benefits and liabilities of using a product line
approach in relation to the case?
\end{question}

\fixme{Answer question 5.2}

\subsection{Product Lines - Question 3}

\begin{question}
Relate Service-Oriented Architecture and Product Lines?
\end{question}

\fixme{Answer question 5.3}

### 2008-03-01 SAiP/Module1/H3/doc/qualityattributes.tex
Formatting of questions completed.

%%%
% Quality Attributes
%%%
\subsection{Quality Attributes -- Beer Web Store}

@@

Discuss:
\begin{itemize}
    \item Describe technique(s) for architectural requirements capture
    that are applicable to the above case
    \item Give feasible architectural requirements for availability
    and performance for the Beer Web Store using such techniques (at
    least one for each quality attribute)
    \item Argue how tactics and/or styles may be used to resolve the requirements
    \item Discuss where Service-Oriented Architecture can play a role
    with respect to the Beer Web Store? Consider the quality implications
    \item Reflect upon what the role of quality attributes in software
    architecture is
\end{itemize}

>>>>

%%%
% Quality Attributes
%%%
\section{Quality Attributes -- Beer Web Store}

@@

\subsection{Quality Attributes - Question 1}

\begin{question}
Describe technique(s) for architectural requirements capture
that are applicable to the above case
\end{question}

\fixme{Answer question 3.1}

\subsection{Quality Attributes - Question 2}

\begin{question}
Give feasible architectural requirements for availability
and performance for the Beer Web Store using such techniques (at
least one for each quality attribute)
\end{question}

\fixme{Answer question 2.2}

\subsection{Quality Attributes - Question 3}

\begin{question}
Argue how tactics and/or styles may be used to resolve the requirements
\end{question}

\fixme{Answer question 3.3}

\subsection{Quality Attributes - Question 4}

\begin{question}
Discuss where Service-Oriented Architecture can play a role
with respect to the Beer Web Store? Consider the quality implications
\end{question}

\fixme{Answer question 3.4}

\subsection{Quality Attributes - Question 5}

\begin{question}
Reflect upon what the role of quality attributes in software
architecture is
\end{question}

\fixme{Answer question 3.5}

### 2008-03-01 SAiP/Module1/H3/doc/softwarearchitecture.tex
Formatting of questions completed.

\subsection{Question 1}
\begin{question}
Outline how you would approach the tasks of creating the
architecture for the Beer Web Store. Consider, e.g., which steps
would you takes and in which order?
\end{question}

@@

\begin{description}
    \item[a. Choose the architectual drivers]
  Here the quality attributes of the system would be defined by the stakeholders of the system and then a vote would be used to determine which of the quality attributes are architectual drivers. The quality attributes would be expressed as quality attribute scenarios.
    \item[b. Choose an architectual pattern]
  Based on the architectual drivers selected in 1, use the mapping in Bass et al. as well as other literature and experience to determine some tactics for achieving the architectual drivers for the system. Then select some architectual patterns to realize the tactics.
    \item[c. Instantiate modules using multiple views]
  Based on the tactics and patterns found above the architecture for the system may be expressed using UML. It is \emph{always} required to use multiple views in order to properly describe the architecture. A good approach is the "3 + 1" structure, which uses three viewpoints; Module viewpoint, Component \& Connector viewpoint and Allocation viewpoint. These three viewpoint is expressed in UML using Package diagrams, Object and sequence diagrams, and deployment diagrams respectively. These diagrams should in the first iteration only look at relations and interactions between the main components (the layers).
    \item[d. Define interfaces]
  Define the interfaces between the main components (the layers).
    \item[e. Verify scenarios and use cases]
  Make sure that the steps a - d covered all the parts of the scenarios. If not include the missing parts and updates the scenarios/architecture is inconsistencies are found.
\end{description}
\subsubsection{Repeat the steps above for every module that needs further decomposition}
The first iteration only look at the overall architecture (the leation and communication between layers). The following iterations will decompose the individual layers and as needed the individual components in the layers.
\subsection{Question 2}

\begin{question}
Give concrete examples of what elements, relations, and structures as defined in \cite{bass2003sa} could be in relation to an architecture for the Beer Web Store.
\end{question}
\subsubsection{Elements}
Based on the present decomposition the elements that are know the layers, where each layer is an element as described below.
\begin{itemize}
    \item[Clients] The clients access the server inorder to perform some action
    \item[Server] The server is accessed by the clients and when needed access the database via its Fa\c cade pattern.
    \item[Database] The database exposes its interface to the server via a Fa\c cade pattern.
\end{itemize}
\fixme{Insert element (class) diagram for the above}
\subsubsection{Relations}
\subsubsection{Strustures}
\subsection{Question 3}
\begin{question}
\emph{Apply \cite{perrywolf1992}'s model of software architecture as
      \begin{quote}
	{\it Software Architecture = \{Elements, Form, Rationale\}}
      \end{quote}
      to the Beer Web System}
\end{question}

\begin{itemize}
    \item Apply [Perry and Wolf, 1992]'s model of software architecture as
      \begin{quote}
	{\it Software Architecture = \{Elements, Form, Rationale\}}
      \end{quote}
      to the Beer Web System
    \item Reflect on what happens if the words ``software'' and
    ``computing'' are removed from the definition of 'software
    architecture' in [Bass et al., 2003]
    \item The architect decides to create a full architecture
    description before embarking on any implementation of the
    system. Discuss pros and cons of taking that approach
\end{itemize}

>>>>

\subsection{Software Architecture - Question 1}
\begin{question}
Outline how you would approach the tasks of creating the
architecture for the Beer Web Store. Consider, e.g., which steps
would you takes and in which order?
\end{question}

@@

\begin{description}
    \item[a. Choose the architectual drivers]
  Here the quality attributes of the system would be defined by the stakeholders of the system and then a vote would be used to determine which of the quality attributes are architectual drivers. The quality attributes would be expressed as quality attribute scenarios.
    \item[b. Choose an architectual pattern]
  Based on the architectual drivers selected in 1, use the mapping in Bass et al. as well as other literature and experience to determine some tactics for achieving the architectual drivers for the system. Then select some architectual patterns to realize the tactics.
    \item[c. Instantiate modules using multiple views]
  Based on the tactics and patterns found above the architecture for the system may be expressed using UML. It is \emph{always} required to use multiple views in order to properly describe the architecture. A good approach is the "3 + 1" structure, which uses three viewpoints; Module viewpoint, Component \& Connector viewpoint and Allocation viewpoint. These three viewpoint is expressed in UML using Package diagrams, Object and sequence diagrams, and deployment diagrams respectively. These diagrams should in the first iteration only look at relations and interactions between the main components (the layers).
    \item[d. Define interfaces]
  Define the interfaces between the main components (the layers).
    \item[e. Verify scenarios and use cases]
  Make sure that the steps a - d covered all the parts of the scenarios. If not include the missing parts and updates the scenarios/architecture is inconsistencies are found.
\end{description}
\subsubsection{Repeat the steps above for every module that needs further decomposition}
The first iteration only look at the overall architecture (the leation and communication between layers). The following iterations will decompose the individual layers and as needed the individual components in the layers.

\subsection{Software Architecture - Question 2}

\begin{question}
Give concrete examples of what elements, relations, and structures as defined in \cite{bass2003sa} could be in relation to an architecture for the Beer Web Store.
\end{question}

\subsubsection{Elements}
Based on the present decomposition the elements that are know the layers, where each layer is an element as described below.
\begin{itemize}
    \item[Clients] The clients access the server inorder to perform some action
    \item[Server] The server is accessed by the clients and when needed access the database via its Fa\c cade pattern.
    \item[Database] The database exposes its interface to the server via a Fa\c cade pattern.
\end{itemize}
\fixme{Insert element (class) diagram for the above}

\subsubsection{Relations}

\fixme{Answer question 1.2}

\subsubsection{Strustures}

\fixme{Answer question 1.2}

\subsection{Software Architecture - Question 3}

\begin{question}
Apply \cite{perrywolf1992}'s model of software architecture as
\begin{quote}
	{\it Software Architecture = \{Elements, Form, Rationale\}}
\end{quote}
to the Beer Web System
\end{question}

\fixme{Answer question 1.3}

\subsection{Software Architecture - Question 4}

\begin{question}
Reflect on what happens if the words ``software'' and
``computing'' are removed from the definition of 'software
architecture' in [Bass et al., 2003]
\end{question}

\fixme{Answer question 1.4}

\subsection{Software Architecture - Question 5}

\begin{question}
The architect decides to create a full architecture
description before embarking on any implementation of the
system. Discuss pros and cons of taking that approach
\end{question}

\fixme{Answer question 1.5}
